---
title: 'Contact tracing with time to action distribution '
author: "Laura Boyle, Dennis Liu, Joshua Ross"
date: "25/09/20"
output:
  pdf_document:
    number_sections: yes
    toc: yes
    toc_depth: 3
  html_document:
    toc: yes
    toc_depth: '3'
    df_print: paged
header-includes: \usepackage{placeins}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.width = 6,
  fig.asp = 0.618,
  out.width = "120%",
  fig.align = "center",
  root.dir = '../'
)
pacman::p_load(tidyverse,readxl,kableExtra,ggplot2,lubridate)
```

\newpage

# Snowball tracing
## n = 20000, offset = 0, gamma mean = 3 variance = 6

```{r, echo=FALSE}

setwd("../data/n_20000_offset_0_gamma_32_2_22.09.20/")

N3 <- read.csv("20000allpc_days_-3_sc3DL.csv")
N2 <- read.csv("20000allpc_days_-2_sc3DL.csv")
N1 <- read.csv("20000allpc_days_-1_sc3DL.csv")
N0 <- read.csv("20000allpc_days_0_sc3DL.csv")
P1 <- read.csv("20000allpc_days_1_sc3DL.csv")
P2 <- read.csv("20000allpc_days_2_sc3DL.csv")

df <- rbind(N3,N2,N1,N0,P1,P2)

```

### Case numbers 

```{r, echo = FALSE}

df %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(mean = mean(`cases`),
            median = median(`cases`),
            min = min(`cases`),
            max = max(`cases`),
            n_sims = n()) %>%
  kable() %>% kable_styling(full_width  = FALSE)

```


```{r, echo = FALSE, crop = NULL, warning = FALSE, fig.height=8}

df %>% 
  filter(`pc`!=0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  mutate(`DAYS` = as.factor(`DAYS`)) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x= efficiency, y=cases, fill = efficiency)) +
  geom_boxplot(outlier.shape=NA) +
  xlab("Days") +  
  facet_wrap(~DAYS) +
  coord_cartesian(ylim = c(0, 2500)) +
  ggtitle("Box plot of cases (axis limited at 5000)")

df %>% 
  filter(`pc`!=0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  mutate(`DAYS` = as.factor(`DAYS`)) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x= efficiency, y=cases, fill = efficiency)) +
  geom_boxplot(outlier.shape=NA) +
  xlab("Days") +  
  facet_wrap(~DAYS) +
  coord_cartesian(ylim = c(0, 150)) +
  ggtitle("Box plot of cases (axis limited at 150)")

#df %>% 
#  mutate(`pc` = as.factor(`pc`)) %>%
#  mutate(`DAYS` = as.factor(`DAYS`)) %>%
#  mutate(efficiency = pc) %>%
#  ggplot(aes(x= efficiency, y=cases, fill = efficiency)) +
#  geom_violin() +
#  xlab("Days") +  
#  facet_wrap(~DAYS) +
#  coord_cartesian(ylim = c(0, 5000)) +
#  ggtitle("Violin plot of cases (axis limited at 5000)")

```

\newpage

```{r, echo = FALSE, crop = NULL}

df %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(mean = mean(`cases`),
            median = median(`cases`),
            min = min(`cases`),
            max = max(`cases`),
            n_sims = n()) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Mean cases") +
  labs(y="mean cases") + scale_color_brewer(palette="Paired") +
  theme_bw()

df %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(mean = mean(`cases`),
            median = median(`cases`),
            min = min(`cases`),
            max = max(`cases`),
            n_sims = n()) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=median, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Median cases") +
  labs(y="median cases") + scale_color_brewer(palette="Paired") +
  theme_bw()

```

\newpage

### Cases prevented 

```{r, echo = FALSE, crop = NULL}

baseline_mean <- df %>%
  filter(pc==0) %>%
  summarise(mean(cases)) 
baseline_mean <- baseline_mean$`mean(cases)`
  
df %>%
  filter(pc > 0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(mean = mean(`cases`)) %>%
  mutate(change_mean = (baseline_mean - mean)/baseline_mean* 100) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=change_mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Mean percentage of cases prevented") +
  labs(y="mean % cases stopped", x="Days relative to symptom onset") + scale_color_brewer(palette="Paired") +
  theme_bw()



```

```{r, echo = FALSE, crop = NULL}

baseline_median <- df %>%
  filter(pc==0) %>%
  summarise(median(cases)) 
baseline_median <- baseline_median$`median(cases)`
  
df %>%
  filter(pc > 0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(median = median(`cases`)) %>%
  mutate(change_mean = (baseline_median - median)/baseline_median* 100) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=change_mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Median percentage of cases prevented") +
  labs(y="median % cases stopped", x="Days relative to symptom onset") + scale_color_brewer(palette="Paired") +
  theme_bw()

```

\newpage

```{r, echo = FALSE, crop = NULL, warning=FALSE}

# df %>%
#   filter(pc > 0) %>%
#   mutate(`pc` = as.factor(`pc`)) %>%
#   group_by(`DAYS`,`pc`) %>%
#   summarise(median = median(`cases`)) %>%
#   mutate(change_median = (baseline_median - median)/baseline_median* 100) %>%
#   mutate(efficiency = pc) %>%
#   filter(DAYS <1) %>%
#   group_by(pc) %>%
#   mutate(Marginal = -(lead(change_median) -change_median)) %>%
#   kable() %>%
#   kable_styling(full_width = FALSE)

plot <- df %>%
  filter(pc > 0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(median = median(`cases`)) %>%
  mutate(change_median = (baseline_median - median)/baseline_median* 100) %>%
  mutate(efficiency = pc) %>%
  filter(DAYS <1) %>%
  group_by(pc) %>%
  mutate(Marginal = -(lead(change_median) -change_median)) %>%
  filter(DAYS <0) %>%
  ggplot(aes(y=Marginal,x=as.factor(DAYS),fill=`efficiency`))+
  geom_col(width=.4, position = "dodge")

plot + theme_bw() +
  labs(y="Marginal benefit from Day x to (x-1)", x="Days relative to symptom onset")

```

\newpage

### Cases prevented (proportion)


```{r, echo = FALSE, crop = NULL}

df %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=prop_cases_prevented_mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Mean proportion of cases prevented") +
  labs(y="mean proportion") + scale_color_brewer(palette="Paired") +
  theme_bw()

```

### Actual generation interval


```{r, echo = FALSE, crop = NULL}

df %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=actual_gen_times_mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Mean generation interval") +
  labs(y="mean generation interval") + scale_color_brewer(palette="Paired") +
  theme_bw()

```

\newpage

## n = 20000, offset = 1, gamma mean = 2 variance = 1


```{r, echo=FALSE}

setwd("../data/n_20000_offset_1_gamma_2.5_.5_22.09.20/")

N3 <- read.csv("allpc_days_-3_sc3DL.csv")
N2 <- read.csv("allpc_days_-2_sc3DL.csv")
N1 <- read.csv("allpc_days_-1_sc3DL.csv")
N0 <- read.csv("allpc_days_0_sc3DL.csv")
P1 <- read.csv("allpc_days_1_sc3DL.csv")
P2 <- read.csv("allpc_days_2_sc3DL.csv")

df2 <- rbind(N3,N2,N1,N0,P1,P2)

```


### Case numbers 


```{r, echo = FALSE}

df2 %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(mean = mean(`cases`),
            median = median(`cases`),
            min = min(`cases`),
            max = max(`cases`),
            n_sims = n()) %>%
  kable() %>% kable_styling(full_width  = FALSE)

```

```{r, echo = FALSE, crop = NULL, warning = FALSE,fig.height=8}

df2 %>% 
  filter(`pc`!=0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  mutate(`DAYS` = as.factor(`DAYS`)) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x= efficiency, y=cases, fill = efficiency)) +
  geom_boxplot(outlier.shape=NA) +
  xlab("Days") +  
  facet_wrap(~DAYS) +
  coord_cartesian(ylim = c(0, 5000)) +
  ggtitle("Box plot of cases (axis limited at 5000)")

df %>% 
  filter(`pc`!=0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  mutate(`DAYS` = as.factor(`DAYS`)) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x= efficiency, y=cases, fill = efficiency)) +
  geom_boxplot(outlier.shape=NA) +
  xlab("Days") +  
  facet_wrap(~DAYS) +
  coord_cartesian(ylim = c(0, 150)) +
  ggtitle("Box plot of cases (axis limited at 150)")

#df2 %>% 
#  mutate(`pc` = as.factor(`pc`)) %>%
#  mutate(`DAYS` = as.factor(`DAYS`)) %>%
#  mutate(efficiency = pc) %>%
#  ggplot(aes(x= efficiency, y=cases, fill = efficiency)) +
#  geom_violin() +
#  xlab("Days") +  
#  facet_wrap(~DAYS) +
#  coord_cartesian(ylim = c(0, 5000)) +
#  ggtitle("Violin plot of cases (axis limited at 5000)")

```

\newpage

```{r, echo = FALSE, crop = NULL}

df2 %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(mean = mean(`cases`),
            median = median(`cases`),
            min = min(`cases`),
            max = max(`cases`),
            n_sims = n()) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Mean cases") +
  labs(y="mean cases") + scale_color_brewer(palette="Paired") +
  theme_bw()

df2 %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(mean = mean(`cases`),
            median = median(`cases`),
            min = min(`cases`),
            max = max(`cases`),
            n_sims = n()) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=median, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Median cases") +
  labs(y="median cases") + scale_color_brewer(palette="Paired") +
  theme_bw()

```

\newpage

### Cases prevented (summary statistics)

```{r, echo = FALSE, crop = NULL}

baseline_mean <- df2 %>%
  filter(pc==0) %>%
  summarise(mean(cases)) 
baseline_mean <- baseline_mean$`mean(cases)`
  
df2 %>%
  filter(pc > 0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(mean = mean(`cases`)) %>%
  mutate(change_mean = (baseline_mean - mean)/baseline_mean* 100) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=change_mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Mean percentage of cases prevented") +
  labs(y="mean % cases stopped", x="Days relative to symptom onset") + scale_color_brewer(palette="Paired") +
  theme_bw()

```

```{r, echo = FALSE, crop = NULL}

baseline_median <- df2 %>%
  filter(pc==0) %>%
  summarise(median(cases)) 
baseline_median <- baseline_median$`median(cases)`
  
df2 %>%
  filter(pc > 0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(median = median(`cases`)) %>%
  mutate(change_mean = (baseline_median - median)/baseline_median* 100) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=change_mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Median percentage of cases prevented") +
  labs(y="median % cases stopped", x="Days relative to symptom onset") + scale_color_brewer(palette="Paired") +
  theme_bw()

```


\newpage

```{r, echo = FALSE, crop = NULL, warning=FALSE}

# df2 %>%
#   filter(pc > 0) %>%
#   mutate(`pc` = as.factor(`pc`)) %>%
#   group_by(`DAYS`,`pc`) %>%
#   summarise(median = median(`cases`)) %>%
#   mutate(change_median = (baseline_median - median)/baseline_median* 100) %>%
#   mutate(efficiency = pc) %>%
#   filter(DAYS <1) %>%
#   group_by(pc) %>%
#   mutate(Marginal = -(lead(change_median) -change_median)) %>%
#   kable() %>%
#   kable_styling(full_width = FALSE)

plot <- df2 %>%
  filter(pc > 0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(median = median(`cases`)) %>%
  mutate(change_median = (baseline_median - median)/baseline_median* 100) %>%
  mutate(efficiency = pc) %>%
  filter(DAYS <1) %>%
  group_by(pc) %>%
  mutate(Marginal = -(lead(change_median) -change_median)) %>%
  filter(DAYS <0) %>%
  ggplot(aes(y=Marginal,x=as.factor(DAYS),fill=`efficiency`))+
  geom_col(width=.4, position = "dodge")

plot + theme_bw() +
  labs(y="Marginal benefit from Day x to (x-1)", x="Days relative to symptom onset")

```


\newpage

### Cases prevented (proportion)


```{r, echo = FALSE, crop = NULL}

df2 %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=prop_cases_prevented_mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Mean proportion of cases prevented") +
  labs(y="mean proportion") + scale_color_brewer(palette="Paired") +
  theme_bw()

```

### Actual generation interval


```{r, echo = FALSE, crop = NULL}

df2 %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=actual_gen_times_mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Mean generation interval") +
  labs(y="mean generation interval") + scale_color_brewer(palette="Paired") +
  theme_bw()

```

\newpage
# Not snowball - Secondary cases traced 

## n = 2000, offset =1, gamma shape = 2, scale = 1 

```{r, echo=FALSE}

setwd("../data/n_20000_offset_1_gamma_2_1_24.09.20/")

N3 <- read.csv("20000allpc_days_-3_sc1DL.csv")
N2 <- read.csv("20000allpc_days_-2_sc1DL.csv")
N1 <- read.csv("20000allpc_days_-1_sc1DL.csv")
N0 <- read.csv("20000allpc_days_0_sc1DL.csv")
P1 <- read.csv("20000allpc_days_1_sc1DL.csv")
P2 <- read.csv("20000allpc_days_2_sc1DL.csv")

df2 <- rbind(N3,N2,N1,N0,P1,P2)

```


### Case numbers 


```{r, echo = FALSE}

df2 %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(mean = mean(`cases`),
            median = median(`cases`),
            min = min(`cases`),
            max = max(`cases`),
            n_sims = n()) %>%
  kable() %>% kable_styling(full_width  = FALSE)

```

```{r, echo = FALSE, crop = NULL, warning = FALSE, fig.height=8}

df2 %>% 
  filter(`pc`!=0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  mutate(`DAYS` = as.factor(`DAYS`)) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x= efficiency, y=cases, fill = efficiency)) +
  geom_boxplot(outlier.shape=NA) +
  xlab("Days") +  
  facet_wrap(~DAYS) +
  coord_cartesian(ylim = c(0, 2500)) +
  ggtitle("Box plot of cases (axis limited at 5000)")

df %>% 
  filter(`pc`!=0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  mutate(`DAYS` = as.factor(`DAYS`)) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x= efficiency, y=cases, fill = efficiency)) +
  geom_boxplot(outlier.shape=NA) +
  xlab("Days") +  
  facet_wrap(~DAYS) +
  coord_cartesian(ylim = c(0, 150)) +
  ggtitle("Box plot of cases (axis limited at 150)")
```

\newpage

```{r, echo = FALSE, crop = NULL}

df2 %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(mean = mean(`cases`),
            median = median(`cases`),
            min = min(`cases`),
            max = max(`cases`),
            n_sims = n()) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Mean cases") +
  labs(y="mean cases") + scale_color_brewer(palette="Paired") +
  theme_bw()

df2 %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(mean = mean(`cases`),
            median = median(`cases`),
            min = min(`cases`),
            max = max(`cases`),
            n_sims = n()) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=median, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Median cases") +
  labs(y="median cases") + scale_color_brewer(palette="Paired") +
  theme_bw()

```

\newpage

### Cases prevented (summary statistics)

```{r, echo = FALSE, crop = NULL}

baseline_mean <- df2 %>%
  filter(pc==0) %>%
  summarise(mean(cases)) 
baseline_mean <- baseline_mean$`mean(cases)`
  
df2 %>%
  filter(pc > 0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(mean = mean(`cases`)) %>%
  mutate(change_mean = (baseline_mean - mean)/baseline_mean* 100) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=change_mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Mean percentage of cases prevented") +
  labs(y="mean % cases stopped", x="Days relative to symptom onset") + scale_color_brewer(palette="Paired") +
  theme_bw()

```

```{r, echo = FALSE, crop = NULL}

baseline_median <- df2 %>%
  filter(pc==0) %>%
  summarise(median(cases)) 
baseline_median <- baseline_median$`median(cases)`
  
df2 %>%
  filter(pc > 0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(median = median(`cases`)) %>%
  mutate(change_mean = (baseline_median - median)/baseline_median* 100) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=change_mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Median percentage of cases prevented") +
  labs(y="median % cases stopped", x="Days relative to symptom onset") + scale_color_brewer(palette="Paired") +
  theme_bw()

```


\newpage

```{r, echo = FALSE, crop = NULL, warning=FALSE}

# df2 %>%
#   filter(pc > 0) %>%
#   mutate(`pc` = as.factor(`pc`)) %>%
#   group_by(`DAYS`,`pc`) %>%
#   summarise(median = median(`cases`)) %>%
#   mutate(change_median = (baseline_median - median)/baseline_median* 100) %>%
#   mutate(efficiency = pc) %>%
#   filter(DAYS <1) %>%
#   group_by(pc) %>%
#   mutate(Marginal = -(lead(change_median) -change_median)) %>%
#   kable() %>%
#   kable_styling(full_width = FALSE)

plot <- df2 %>%
  filter(pc > 0) %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  summarise(median = median(`cases`)) %>%
  mutate(change_median = (baseline_median - median)/baseline_median* 100) %>%
  mutate(efficiency = pc) %>%
  filter(DAYS <1) %>%
  group_by(pc) %>%
  mutate(Marginal = -(lead(change_median) -change_median)) %>%
  filter(DAYS <0) %>%
  ggplot(aes(y=Marginal,x=as.factor(DAYS),fill=`efficiency`))+
  geom_col(width=.4, position = "dodge")

plot + theme_bw() +
  labs(y="Marginal benefit from Day x to (x-1)", x="Days relative to symptom onset")

```


\newpage

### Cases prevented (proportion)


```{r, echo = FALSE, crop = NULL}

df2 %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=prop_cases_prevented_mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Mean proportion of cases prevented") +
  labs(y="mean proportion") + scale_color_brewer(palette="Paired") +
  theme_bw()

```

### Actual generation interval


```{r, echo = FALSE, crop = NULL}

df2 %>%
  mutate(`pc` = as.factor(`pc`)) %>%
  group_by(`DAYS`,`pc`) %>%
  mutate(efficiency = pc) %>%
  ggplot(aes(x=`DAYS`, y=actual_gen_times_mean, group=`efficiency`)) +
  geom_line(aes(color=`efficiency`)) +
  geom_point(aes(color=`efficiency`)) +
  ggtitle("Mean generation interval") +
  labs(y="mean generation interval") + scale_color_brewer(palette="Paired") +
  theme_bw()

```
